### 2021-10-29 forecast/code/figures/compare-to-hub-ryan.Rmd
Filter to ahead <= 21

p1 <- plotter(ours3,
        "wis", Mean, scaler = "strawman_wis", 
        order_of_operations = c("aggr","scale")) +
  ylab("Mean WIS (relative to baseline)")

p2 <- plotter(ours3,
        "wis", GeoMean, scaler = "strawman_wis", 
        order_of_operations = c("aggr","scale")) +
  ylab("Geometric mean WIS (relative to baseline)")

@@

fig3 <- plotter(fcasts_honest, 
        "wis", Mean, scaler = "strawman_wis", 
        order_of_operations = c("aggr","scale")) +
  ylab("Mean WIS (relative to baseline)")
fig3
```

>>>>

p1 <- plotter(ours3 %>% filter(ahead <= 21), 
        "wis", Mean, scaler = "strawman_wis", 
        order_of_operations = c("aggr","scale")) +
  ylab("Mean WIS (relative to baseline)")

p2 <- plotter(ours3 %>% filter(ahead <= 21), 
        "wis", GeoMean, scaler = "strawman_wis", 
        order_of_operations = c("aggr","scale")) +
  ylab("Geometric mean WIS (relative to baseline)")

@@

fig3 <- plotter(fcasts_honest %>% filter(ahead <= 21), 
        "wis", Mean, scaler = "strawman_wis", 
        order_of_operations = c("aggr","scale")) +
  ylab("Mean WIS (relative to baseline)")
fig3
```
